---
output:
  github_document:
    html_preview: false
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
options(tibble.print_min = 5, tibble.print_max = 5)
```

## tidyfec

The tidyfec package aims to make campaign finance data more accessible in R and friendly with tidy workflows. It works by accessing data through the [OpenFEC API](https://api.open.fec.gov/developers/), which requires an [API key](https://api.data.gov/signup/) to run.

## Installation

Though I'm developing out in the open, this is very much pre-alpha release status. Installation is through the devtools package

```{r, eval = FALSE}
install.packages("devtools")
devtools::install_github("stephenholzman/tidyfec")
```

## Examples
Search for a candidates by name.

```{r}
library(tidyfec)
library(tidyverse)
source("data.gov.key")
search_on_name <- tidyfec::search_candidates(api_key = api_key, name = "Obama", data_structure = "tidy")

head(search_on_name)

```

Search for a specific election.

```{r}
search_on_election <- tidyfec::search_candidates(api_key = api_key, state = "VA", district = "05", office = "H", election_year = "2018", data_structure = "tidy")

head(search_on_election)
```

