---
title: "Get Aggregated Data"
author: "Stephen Holzman"
date: "5/30/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

These functions cover anything that isn't itemized data. Want to know how much money a candidate has raised? Look at data from every filing their committee has ever made? How much outside money has been spent in an election?

As shown in these examples, the tidyusafec suggested workflow is to pipe (`%>%`) the results of a function with the `search_` prefix into a function with the `get_` prefix.

- `get_candidate_totals()` by default currently returns a tibble with information about a candidate's funding totals, what you would typically see on the summary tables of the FEC site. 
- `get_committee_reports()` by default currently returns a tibble with information about committee reports. Mostly useful for looking at quarterly report trends.
- `get_election_summary()` by default currently returns a tibble with financial summaries by election.



### Setup Libraries and API Keys

```{r, eval = FALSE}
library(tidyverse)
library(tidyusafec)

save_datagov_apikey(key = "DATA.GOV KEY STRING")
```

## get_candidate_totals()

Each row of the tibble returned is a specific total given in the `amount` column. The `type_of_funds` column shows what that amount applies to. While you can use the function by itself, piping the results of `search_candidates` will automatically join additional columns with context like name, office, state, etc.

### Get Totals for Candidates Currently in a Particular Race

```{r, results='asis', eval = FALSE}
va_05_house_candidates <- search_candidates(election_year = 2018, office = "H", state = "VA", district = "05", candidate_status = "C") %>%
  get_candidate_totals()
```
```{r, eval = FALSE, include = FALSE, results='asis'}
select(va_05_house_candidates[1:20,], -principal_committees) %>%
  knitr::kable(format = "html") %>%
  kableExtra::kable_styling() %>%
  kableExtra::scroll_box(width = "100%", height = "200px")
```


<div style="border: 1px solid #ddd; padding: 5px; overflow-y: scroll; height:200px; overflow-x: scroll; width:100%; "><table class="table" style="margin-left: auto; margin-right: auto;">
 <thead>
  <tr>
   <th style="text-align:left;"> candidate_id </th>
   <th style="text-align:left;"> coverage_start_date </th>
   <th style="text-align:left;"> full_election </th>
   <th style="text-align:left;"> coverage_end_date </th>
   <th style="text-align:right;"> last_report_year </th>
   <th style="text-align:right;"> cycle </th>
   <th style="text-align:left;"> last_report_type_full </th>
   <th style="text-align:left;"> last_beginning_image_number </th>
   <th style="text-align:left;"> type_of_funds </th>
   <th style="text-align:right;"> amount </th>
   <th style="text-align:left;"> load_date </th>
   <th style="text-align:left;"> last_file_date </th>
   <th style="text-align:left;"> election_years </th>
   <th style="text-align:left;"> party </th>
   <th style="text-align:left;"> candidate_status </th>
   <th style="text-align:left;"> office_full </th>
   <th style="text-align:left;"> state </th>
   <th style="text-align:left;"> federal_funds_flag </th>
   <th style="text-align:left;"> has_raised_funds </th>
   <th style="text-align:left;"> office </th>
   <th style="text-align:left;"> election_districts </th>
   <th style="text-align:left;"> name </th>
   <th style="text-align:right;"> district_number </th>
   <th style="text-align:left;"> cycles </th>
   <th style="text-align:left;"> incumbent_challenge </th>
   <th style="text-align:left;"> party_full </th>
   <th style="text-align:left;"> first_file_date </th>
   <th style="text-align:right;"> active_through </th>
   <th style="text-align:left;"> incumbent_challenge_full </th>
   <th style="text-align:left;"> last_f2_date </th>
   <th style="text-align:left;"> district </th>
   <th style="text-align:left;"> committee_id </th>
   <th style="text-align:left;"> committee_name </th>
   <th style="text-align:left;"> treasurer_name </th>
   <th style="text-align:right;"> earliest_cycle </th>
   <th style="text-align:right;"> latest_cycle </th>
   <th style="text-align:right;"> earliest_election_year </th>
   <th style="text-align:right;"> latest_election_year </th>
  </tr>
 </thead>
<tbody>
  <tr>
   <td style="text-align:left;"> H8VA05155 </td>
   <td style="text-align:left;"> 2017-07-13T00:00:00+00:00 </td>
   <td style="text-align:left;"> TRUE </td>
   <td style="text-align:left;"> 2018-04-15T00:00:00+00:00 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:left;"> PRE-CONVENTION </td>
   <td style="text-align:left;"> 201804239111720149 </td>
   <td style="text-align:left;"> loan_repayments </td>
   <td style="text-align:right;"> 0.00 </td>
   <td style="text-align:left;"> 2017-10-16T21:00:02 </td>
   <td style="text-align:left;"> 2017-07-24 </td>
   <td style="text-align:left;"> list(2018) </td>
   <td style="text-align:left;"> DEM </td>
   <td style="text-align:left;"> C </td>
   <td style="text-align:left;"> House </td>
   <td style="text-align:left;"> VA </td>
   <td style="text-align:left;"> FALSE </td>
   <td style="text-align:left;"> TRUE </td>
   <td style="text-align:left;"> H </td>
   <td style="text-align:left;"> list("05") </td>
   <td style="text-align:left;"> COCKBURN, LESLIE </td>
   <td style="text-align:right;"> 5 </td>
   <td style="text-align:left;"> list(2018) </td>
   <td style="text-align:left;"> C </td>
   <td style="text-align:left;"> DEMOCRATIC PARTY </td>
   <td style="text-align:left;"> 2017-07-13 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:left;"> Challenger </td>
   <td style="text-align:left;"> 2017-07-24 </td>
   <td style="text-align:left;"> 05 </td>
   <td style="text-align:left;"> C00650366 </td>
   <td style="text-align:left;"> LESLIE COCKBURN FOR CONGRESS </td>
   <td style="text-align:left;"> MELE, STEVE </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> H8VA05148 </td>
   <td style="text-align:left;"> 2017-07-01T00:00:00+00:00 </td>
   <td style="text-align:left;"> TRUE </td>
   <td style="text-align:left;"> 2018-04-15T00:00:00+00:00 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:left;"> PRE-CONVENTION </td>
   <td style="text-align:left;"> 201804209110419709 </td>
   <td style="text-align:left;"> loan_repayments </td>
   <td style="text-align:right;"> 0.00 </td>
   <td style="text-align:left;"> 2017-10-24T21:01:05 </td>
   <td style="text-align:left;"> 2017-07-02 </td>
   <td style="text-align:left;"> list(2018) </td>
   <td style="text-align:left;"> DEM </td>
   <td style="text-align:left;"> C </td>
   <td style="text-align:left;"> House </td>
   <td style="text-align:left;"> VA </td>
   <td style="text-align:left;"> FALSE </td>
   <td style="text-align:left;"> TRUE </td>
   <td style="text-align:left;"> H </td>
   <td style="text-align:left;"> list("05") </td>
   <td style="text-align:left;"> CULLOP, BENJAMIN NIEL </td>
   <td style="text-align:right;"> 5 </td>
   <td style="text-align:left;"> list(2018) </td>
   <td style="text-align:left;"> C </td>
   <td style="text-align:left;"> DEMOCRATIC PARTY </td>
   <td style="text-align:left;"> 2017-07-02 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:left;"> Challenger </td>
   <td style="text-align:left;"> 2017-07-02 </td>
   <td style="text-align:left;"> 05 </td>
   <td style="text-align:left;"> C00649020 </td>
   <td style="text-align:left;"> CULLOP FOR CONGRESS </td>
   <td style="text-align:left;"> VANDEVER, JASON </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> H6VA05142 </td>
   <td style="text-align:left;"> 2017-01-01T00:00:00+00:00 </td>
   <td style="text-align:left;"> TRUE </td>
   <td style="text-align:left;"> 2018-04-08T00:00:00+00:00 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:left;"> PRE-CONVENTION </td>
   <td style="text-align:left;"> 201804169108269935 </td>
   <td style="text-align:left;"> loan_repayments </td>
   <td style="text-align:right;"> 0.00 </td>
   <td style="text-align:left;"> 2017-05-23T07:10:20 </td>
   <td style="text-align:left;"> 2017-05-16 </td>
   <td style="text-align:left;"> list(2016, 2018) </td>
   <td style="text-align:left;"> REP </td>
   <td style="text-align:left;"> C </td>
   <td style="text-align:left;"> House </td>
   <td style="text-align:left;"> VA </td>
   <td style="text-align:left;"> FALSE </td>
   <td style="text-align:left;"> TRUE </td>
   <td style="text-align:left;"> H </td>
   <td style="text-align:left;"> list("05", "05") </td>
   <td style="text-align:left;"> GARRETT, THOMAS ALEXANDER MR. JR. </td>
   <td style="text-align:right;"> 5 </td>
   <td style="text-align:left;"> list(2016, 2018) </td>
   <td style="text-align:left;"> I </td>
   <td style="text-align:left;"> REPUBLICAN PARTY </td>
   <td style="text-align:left;"> 2016-01-27 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:left;"> Incumbent </td>
   <td style="text-align:left;"> 2017-05-16 </td>
   <td style="text-align:left;"> 05 </td>
   <td style="text-align:left;"> C00607101 </td>
   <td style="text-align:left;"> TOM GARRETT FOR CONGRESS </td>
   <td style="text-align:left;"> WOODFIN, CHRISTOPHER MONTGOMERY MR. ESQ. </td>
   <td style="text-align:right;"> 2016 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2016 </td>
   <td style="text-align:right;"> 2018 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> H6VA05142 </td>
   <td style="text-align:left;"> 2016-01-01T00:00:00+00:00 </td>
   <td style="text-align:left;"> TRUE </td>
   <td style="text-align:left;"> 2016-12-31T00:00:00+00:00 </td>
   <td style="text-align:right;"> 2016 </td>
   <td style="text-align:right;"> 2016 </td>
   <td style="text-align:left;"> YEAR-END </td>
   <td style="text-align:left;"> 201702029042407932 </td>
   <td style="text-align:left;"> loan_repayments </td>
   <td style="text-align:right;"> 20000.00 </td>
   <td style="text-align:left;"> 2017-05-23T07:10:20 </td>
   <td style="text-align:left;"> 2017-05-16 </td>
   <td style="text-align:left;"> list(2016, 2018) </td>
   <td style="text-align:left;"> REP </td>
   <td style="text-align:left;"> C </td>
   <td style="text-align:left;"> House </td>
   <td style="text-align:left;"> VA </td>
   <td style="text-align:left;"> FALSE </td>
   <td style="text-align:left;"> TRUE </td>
   <td style="text-align:left;"> H </td>
   <td style="text-align:left;"> list("05", "05") </td>
   <td style="text-align:left;"> GARRETT, THOMAS ALEXANDER MR. JR. </td>
   <td style="text-align:right;"> 5 </td>
   <td style="text-align:left;"> list(2016, 2018) </td>
   <td style="text-align:left;"> I </td>
   <td style="text-align:left;"> REPUBLICAN PARTY </td>
   <td style="text-align:left;"> 2016-01-27 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:left;"> Incumbent </td>
   <td style="text-align:left;"> 2017-05-16 </td>
   <td style="text-align:left;"> 05 </td>
   <td style="text-align:left;"> C00607101 </td>
   <td style="text-align:left;"> TOM GARRETT FOR CONGRESS </td>
   <td style="text-align:left;"> WOODFIN, CHRISTOPHER MONTGOMERY MR. ESQ. </td>
   <td style="text-align:right;"> 2016 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2016 </td>
   <td style="text-align:right;"> 2018 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> H8VA05114 </td>
   <td style="text-align:left;"> 2017-04-01T00:00:00+00:00 </td>
   <td style="text-align:left;"> TRUE </td>
   <td style="text-align:left;"> 2018-04-15T00:00:00+00:00 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:left;"> PRE-CONVENTION </td>
   <td style="text-align:left;"> 201804239111725619 </td>
   <td style="text-align:left;"> loan_repayments </td>
   <td style="text-align:right;"> 0.00 </td>
   <td style="text-align:left;"> 2017-10-01T20:55:35 </td>
   <td style="text-align:left;"> 2017-10-01 </td>
   <td style="text-align:left;"> list(2018) </td>
   <td style="text-align:left;"> DEM </td>
   <td style="text-align:left;"> C </td>
   <td style="text-align:left;"> House </td>
   <td style="text-align:left;"> VA </td>
   <td style="text-align:left;"> FALSE </td>
   <td style="text-align:left;"> TRUE </td>
   <td style="text-align:left;"> H </td>
   <td style="text-align:left;"> list("05") </td>
   <td style="text-align:left;"> HUFFSTETLER, ROGER DEAN RD </td>
   <td style="text-align:right;"> 5 </td>
   <td style="text-align:left;"> list(2018) </td>
   <td style="text-align:left;"> C </td>
   <td style="text-align:left;"> DEMOCRATIC PARTY </td>
   <td style="text-align:left;"> 2017-04-18 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:left;"> Challenger </td>
   <td style="text-align:left;"> 2017-10-01 </td>
   <td style="text-align:left;"> 05 </td>
   <td style="text-align:left;"> C00637918 </td>
   <td style="text-align:left;"> FRIENDS OF RD </td>
   <td style="text-align:left;"> JOHNSON, SARAH </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> H8VA05130 </td>
   <td style="text-align:left;"> 2017-04-01T00:00:00+00:00 </td>
   <td style="text-align:left;"> TRUE </td>
   <td style="text-align:left;"> 2018-03-31T00:00:00+00:00 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:left;"> APRIL QUARTERLY </td>
   <td style="text-align:left;"> 201804139108013236 </td>
   <td style="text-align:left;"> loan_repayments </td>
   <td style="text-align:right;"> 0.00 </td>
   <td style="text-align:left;"> 2017-10-16T21:00:02 </td>
   <td style="text-align:left;"> 2017-05-26 </td>
   <td style="text-align:left;"> list(2018) </td>
   <td style="text-align:left;"> DEM </td>
   <td style="text-align:left;"> C </td>
   <td style="text-align:left;"> House </td>
   <td style="text-align:left;"> VA </td>
   <td style="text-align:left;"> FALSE </td>
   <td style="text-align:left;"> TRUE </td>
   <td style="text-align:left;"> H </td>
   <td style="text-align:left;"> list("05") </td>
   <td style="text-align:left;"> SLATE, ADAM </td>
   <td style="text-align:right;"> 5 </td>
   <td style="text-align:left;"> list(2018) </td>
   <td style="text-align:left;"> C </td>
   <td style="text-align:left;"> DEMOCRATIC PARTY </td>
   <td style="text-align:left;"> 2017-05-26 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:left;"> Challenger </td>
   <td style="text-align:left;"> 2017-05-26 </td>
   <td style="text-align:left;"> 05 </td>
   <td style="text-align:left;"> C00639153 </td>
   <td style="text-align:left;"> ADAM SLATE FOR CONGRESS </td>
   <td style="text-align:left;"> MCREYNOLDS, JAMES M. </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> H8VA05122 </td>
   <td style="text-align:left;"> 2017-04-01T00:00:00+00:00 </td>
   <td style="text-align:left;"> TRUE </td>
   <td style="text-align:left;"> 2018-03-31T00:00:00+00:00 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:left;"> APRIL QUARTERLY </td>
   <td style="text-align:left;"> 201804159108200524 </td>
   <td style="text-align:left;"> loan_repayments </td>
   <td style="text-align:right;"> 0.00 </td>
   <td style="text-align:left;"> 2017-09-27T20:56:17 </td>
   <td style="text-align:left;"> 2017-05-17 </td>
   <td style="text-align:left;"> list(2018) </td>
   <td style="text-align:left;"> DEM </td>
   <td style="text-align:left;"> C </td>
   <td style="text-align:left;"> House </td>
   <td style="text-align:left;"> VA </td>
   <td style="text-align:left;"> FALSE </td>
   <td style="text-align:left;"> TRUE </td>
   <td style="text-align:left;"> H </td>
   <td style="text-align:left;"> list("05") </td>
   <td style="text-align:left;"> SNEATHERN, ANDREW </td>
   <td style="text-align:right;"> 5 </td>
   <td style="text-align:left;"> list(2018) </td>
   <td style="text-align:left;"> C </td>
   <td style="text-align:left;"> DEMOCRATIC PARTY </td>
   <td style="text-align:left;"> 2017-05-17 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:left;"> Challenger </td>
   <td style="text-align:left;"> 2017-05-17 </td>
   <td style="text-align:left;"> 05 </td>
   <td style="text-align:left;"> C00640698 </td>
   <td style="text-align:left;"> SNEATHERN FOR CONGRESS </td>
   <td style="text-align:left;"> PAULE-CARRES, PATTI </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> H8VA05155 </td>
   <td style="text-align:left;"> 2017-07-13T00:00:00+00:00 </td>
   <td style="text-align:left;"> TRUE </td>
   <td style="text-align:left;"> 2018-04-15T00:00:00+00:00 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:left;"> PRE-CONVENTION </td>
   <td style="text-align:left;"> 201804239111720149 </td>
   <td style="text-align:left;"> last_net_operating_expenditures </td>
   <td style="text-align:right;"> 42137.83 </td>
   <td style="text-align:left;"> 2017-10-16T21:00:02 </td>
   <td style="text-align:left;"> 2017-07-24 </td>
   <td style="text-align:left;"> list(2018) </td>
   <td style="text-align:left;"> DEM </td>
   <td style="text-align:left;"> C </td>
   <td style="text-align:left;"> House </td>
   <td style="text-align:left;"> VA </td>
   <td style="text-align:left;"> FALSE </td>
   <td style="text-align:left;"> TRUE </td>
   <td style="text-align:left;"> H </td>
   <td style="text-align:left;"> list("05") </td>
   <td style="text-align:left;"> COCKBURN, LESLIE </td>
   <td style="text-align:right;"> 5 </td>
   <td style="text-align:left;"> list(2018) </td>
   <td style="text-align:left;"> C </td>
   <td style="text-align:left;"> DEMOCRATIC PARTY </td>
   <td style="text-align:left;"> 2017-07-13 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:left;"> Challenger </td>
   <td style="text-align:left;"> 2017-07-24 </td>
   <td style="text-align:left;"> 05 </td>
   <td style="text-align:left;"> C00650366 </td>
   <td style="text-align:left;"> LESLIE COCKBURN FOR CONGRESS </td>
   <td style="text-align:left;"> MELE, STEVE </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> H8VA05148 </td>
   <td style="text-align:left;"> 2017-07-01T00:00:00+00:00 </td>
   <td style="text-align:left;"> TRUE </td>
   <td style="text-align:left;"> 2018-04-15T00:00:00+00:00 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:left;"> PRE-CONVENTION </td>
   <td style="text-align:left;"> 201804209110419709 </td>
   <td style="text-align:left;"> last_net_operating_expenditures </td>
   <td style="text-align:right;"> 28287.72 </td>
   <td style="text-align:left;"> 2017-10-24T21:01:05 </td>
   <td style="text-align:left;"> 2017-07-02 </td>
   <td style="text-align:left;"> list(2018) </td>
   <td style="text-align:left;"> DEM </td>
   <td style="text-align:left;"> C </td>
   <td style="text-align:left;"> House </td>
   <td style="text-align:left;"> VA </td>
   <td style="text-align:left;"> FALSE </td>
   <td style="text-align:left;"> TRUE </td>
   <td style="text-align:left;"> H </td>
   <td style="text-align:left;"> list("05") </td>
   <td style="text-align:left;"> CULLOP, BENJAMIN NIEL </td>
   <td style="text-align:right;"> 5 </td>
   <td style="text-align:left;"> list(2018) </td>
   <td style="text-align:left;"> C </td>
   <td style="text-align:left;"> DEMOCRATIC PARTY </td>
   <td style="text-align:left;"> 2017-07-02 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:left;"> Challenger </td>
   <td style="text-align:left;"> 2017-07-02 </td>
   <td style="text-align:left;"> 05 </td>
   <td style="text-align:left;"> C00649020 </td>
   <td style="text-align:left;"> CULLOP FOR CONGRESS </td>
   <td style="text-align:left;"> VANDEVER, JASON </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> H6VA05142 </td>
   <td style="text-align:left;"> 2017-01-01T00:00:00+00:00 </td>
   <td style="text-align:left;"> TRUE </td>
   <td style="text-align:left;"> 2018-04-08T00:00:00+00:00 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:left;"> PRE-CONVENTION </td>
   <td style="text-align:left;"> 201804169108269935 </td>
   <td style="text-align:left;"> last_net_operating_expenditures </td>
   <td style="text-align:right;"> 11516.07 </td>
   <td style="text-align:left;"> 2017-05-23T07:10:20 </td>
   <td style="text-align:left;"> 2017-05-16 </td>
   <td style="text-align:left;"> list(2016, 2018) </td>
   <td style="text-align:left;"> REP </td>
   <td style="text-align:left;"> C </td>
   <td style="text-align:left;"> House </td>
   <td style="text-align:left;"> VA </td>
   <td style="text-align:left;"> FALSE </td>
   <td style="text-align:left;"> TRUE </td>
   <td style="text-align:left;"> H </td>
   <td style="text-align:left;"> list("05", "05") </td>
   <td style="text-align:left;"> GARRETT, THOMAS ALEXANDER MR. JR. </td>
   <td style="text-align:right;"> 5 </td>
   <td style="text-align:left;"> list(2016, 2018) </td>
   <td style="text-align:left;"> I </td>
   <td style="text-align:left;"> REPUBLICAN PARTY </td>
   <td style="text-align:left;"> 2016-01-27 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:left;"> Incumbent </td>
   <td style="text-align:left;"> 2017-05-16 </td>
   <td style="text-align:left;"> 05 </td>
   <td style="text-align:left;"> C00607101 </td>
   <td style="text-align:left;"> TOM GARRETT FOR CONGRESS </td>
   <td style="text-align:left;"> WOODFIN, CHRISTOPHER MONTGOMERY MR. ESQ. </td>
   <td style="text-align:right;"> 2016 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2016 </td>
   <td style="text-align:right;"> 2018 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> H6VA05142 </td>
   <td style="text-align:left;"> 2016-01-01T00:00:00+00:00 </td>
   <td style="text-align:left;"> TRUE </td>
   <td style="text-align:left;"> 2016-12-31T00:00:00+00:00 </td>
   <td style="text-align:right;"> 2016 </td>
   <td style="text-align:right;"> 2016 </td>
   <td style="text-align:left;"> YEAR-END </td>
   <td style="text-align:left;"> 201702029042407932 </td>
   <td style="text-align:left;"> last_net_operating_expenditures </td>
   <td style="text-align:right;"> 34037.67 </td>
   <td style="text-align:left;"> 2017-05-23T07:10:20 </td>
   <td style="text-align:left;"> 2017-05-16 </td>
   <td style="text-align:left;"> list(2016, 2018) </td>
   <td style="text-align:left;"> REP </td>
   <td style="text-align:left;"> C </td>
   <td style="text-align:left;"> House </td>
   <td style="text-align:left;"> VA </td>
   <td style="text-align:left;"> FALSE </td>
   <td style="text-align:left;"> TRUE </td>
   <td style="text-align:left;"> H </td>
   <td style="text-align:left;"> list("05", "05") </td>
   <td style="text-align:left;"> GARRETT, THOMAS ALEXANDER MR. JR. </td>
   <td style="text-align:right;"> 5 </td>
   <td style="text-align:left;"> list(2016, 2018) </td>
   <td style="text-align:left;"> I </td>
   <td style="text-align:left;"> REPUBLICAN PARTY </td>
   <td style="text-align:left;"> 2016-01-27 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:left;"> Incumbent </td>
   <td style="text-align:left;"> 2017-05-16 </td>
   <td style="text-align:left;"> 05 </td>
   <td style="text-align:left;"> C00607101 </td>
   <td style="text-align:left;"> TOM GARRETT FOR CONGRESS </td>
   <td style="text-align:left;"> WOODFIN, CHRISTOPHER MONTGOMERY MR. ESQ. </td>
   <td style="text-align:right;"> 2016 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2016 </td>
   <td style="text-align:right;"> 2018 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> H8VA05114 </td>
   <td style="text-align:left;"> 2017-04-01T00:00:00+00:00 </td>
   <td style="text-align:left;"> TRUE </td>
   <td style="text-align:left;"> 2018-04-15T00:00:00+00:00 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:left;"> PRE-CONVENTION </td>
   <td style="text-align:left;"> 201804239111725619 </td>
   <td style="text-align:left;"> last_net_operating_expenditures </td>
   <td style="text-align:right;"> 58715.92 </td>
   <td style="text-align:left;"> 2017-10-01T20:55:35 </td>
   <td style="text-align:left;"> 2017-10-01 </td>
   <td style="text-align:left;"> list(2018) </td>
   <td style="text-align:left;"> DEM </td>
   <td style="text-align:left;"> C </td>
   <td style="text-align:left;"> House </td>
   <td style="text-align:left;"> VA </td>
   <td style="text-align:left;"> FALSE </td>
   <td style="text-align:left;"> TRUE </td>
   <td style="text-align:left;"> H </td>
   <td style="text-align:left;"> list("05") </td>
   <td style="text-align:left;"> HUFFSTETLER, ROGER DEAN RD </td>
   <td style="text-align:right;"> 5 </td>
   <td style="text-align:left;"> list(2018) </td>
   <td style="text-align:left;"> C </td>
   <td style="text-align:left;"> DEMOCRATIC PARTY </td>
   <td style="text-align:left;"> 2017-04-18 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:left;"> Challenger </td>
   <td style="text-align:left;"> 2017-10-01 </td>
   <td style="text-align:left;"> 05 </td>
   <td style="text-align:left;"> C00637918 </td>
   <td style="text-align:left;"> FRIENDS OF RD </td>
   <td style="text-align:left;"> JOHNSON, SARAH </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> H8VA05130 </td>
   <td style="text-align:left;"> 2017-04-01T00:00:00+00:00 </td>
   <td style="text-align:left;"> TRUE </td>
   <td style="text-align:left;"> 2018-03-31T00:00:00+00:00 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:left;"> APRIL QUARTERLY </td>
   <td style="text-align:left;"> 201804139108013236 </td>
   <td style="text-align:left;"> last_net_operating_expenditures </td>
   <td style="text-align:right;"> 61.11 </td>
   <td style="text-align:left;"> 2017-10-16T21:00:02 </td>
   <td style="text-align:left;"> 2017-05-26 </td>
   <td style="text-align:left;"> list(2018) </td>
   <td style="text-align:left;"> DEM </td>
   <td style="text-align:left;"> C </td>
   <td style="text-align:left;"> House </td>
   <td style="text-align:left;"> VA </td>
   <td style="text-align:left;"> FALSE </td>
   <td style="text-align:left;"> TRUE </td>
   <td style="text-align:left;"> H </td>
   <td style="text-align:left;"> list("05") </td>
   <td style="text-align:left;"> SLATE, ADAM </td>
   <td style="text-align:right;"> 5 </td>
   <td style="text-align:left;"> list(2018) </td>
   <td style="text-align:left;"> C </td>
   <td style="text-align:left;"> DEMOCRATIC PARTY </td>
   <td style="text-align:left;"> 2017-05-26 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:left;"> Challenger </td>
   <td style="text-align:left;"> 2017-05-26 </td>
   <td style="text-align:left;"> 05 </td>
   <td style="text-align:left;"> C00639153 </td>
   <td style="text-align:left;"> ADAM SLATE FOR CONGRESS </td>
   <td style="text-align:left;"> MCREYNOLDS, JAMES M. </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> H8VA05122 </td>
   <td style="text-align:left;"> 2017-04-01T00:00:00+00:00 </td>
   <td style="text-align:left;"> TRUE </td>
   <td style="text-align:left;"> 2018-03-31T00:00:00+00:00 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:left;"> APRIL QUARTERLY </td>
   <td style="text-align:left;"> 201804159108200524 </td>
   <td style="text-align:left;"> last_net_operating_expenditures </td>
   <td style="text-align:right;"> 89583.63 </td>
   <td style="text-align:left;"> 2017-09-27T20:56:17 </td>
   <td style="text-align:left;"> 2017-05-17 </td>
   <td style="text-align:left;"> list(2018) </td>
   <td style="text-align:left;"> DEM </td>
   <td style="text-align:left;"> C </td>
   <td style="text-align:left;"> House </td>
   <td style="text-align:left;"> VA </td>
   <td style="text-align:left;"> FALSE </td>
   <td style="text-align:left;"> TRUE </td>
   <td style="text-align:left;"> H </td>
   <td style="text-align:left;"> list("05") </td>
   <td style="text-align:left;"> SNEATHERN, ANDREW </td>
   <td style="text-align:right;"> 5 </td>
   <td style="text-align:left;"> list(2018) </td>
   <td style="text-align:left;"> C </td>
   <td style="text-align:left;"> DEMOCRATIC PARTY </td>
   <td style="text-align:left;"> 2017-05-17 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:left;"> Challenger </td>
   <td style="text-align:left;"> 2017-05-17 </td>
   <td style="text-align:left;"> 05 </td>
   <td style="text-align:left;"> C00640698 </td>
   <td style="text-align:left;"> SNEATHERN FOR CONGRESS </td>
   <td style="text-align:left;"> PAULE-CARRES, PATTI </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> H8VA05155 </td>
   <td style="text-align:left;"> 2017-07-13T00:00:00+00:00 </td>
   <td style="text-align:left;"> TRUE </td>
   <td style="text-align:left;"> 2018-04-15T00:00:00+00:00 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:left;"> PRE-CONVENTION </td>
   <td style="text-align:left;"> 201804239111720149 </td>
   <td style="text-align:left;"> transfers_from_other_authorized_committee </td>
   <td style="text-align:right;"> 0.00 </td>
   <td style="text-align:left;"> 2017-10-16T21:00:02 </td>
   <td style="text-align:left;"> 2017-07-24 </td>
   <td style="text-align:left;"> list(2018) </td>
   <td style="text-align:left;"> DEM </td>
   <td style="text-align:left;"> C </td>
   <td style="text-align:left;"> House </td>
   <td style="text-align:left;"> VA </td>
   <td style="text-align:left;"> FALSE </td>
   <td style="text-align:left;"> TRUE </td>
   <td style="text-align:left;"> H </td>
   <td style="text-align:left;"> list("05") </td>
   <td style="text-align:left;"> COCKBURN, LESLIE </td>
   <td style="text-align:right;"> 5 </td>
   <td style="text-align:left;"> list(2018) </td>
   <td style="text-align:left;"> C </td>
   <td style="text-align:left;"> DEMOCRATIC PARTY </td>
   <td style="text-align:left;"> 2017-07-13 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:left;"> Challenger </td>
   <td style="text-align:left;"> 2017-07-24 </td>
   <td style="text-align:left;"> 05 </td>
   <td style="text-align:left;"> C00650366 </td>
   <td style="text-align:left;"> LESLIE COCKBURN FOR CONGRESS </td>
   <td style="text-align:left;"> MELE, STEVE </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> H8VA05148 </td>
   <td style="text-align:left;"> 2017-07-01T00:00:00+00:00 </td>
   <td style="text-align:left;"> TRUE </td>
   <td style="text-align:left;"> 2018-04-15T00:00:00+00:00 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:left;"> PRE-CONVENTION </td>
   <td style="text-align:left;"> 201804209110419709 </td>
   <td style="text-align:left;"> transfers_from_other_authorized_committee </td>
   <td style="text-align:right;"> 0.00 </td>
   <td style="text-align:left;"> 2017-10-24T21:01:05 </td>
   <td style="text-align:left;"> 2017-07-02 </td>
   <td style="text-align:left;"> list(2018) </td>
   <td style="text-align:left;"> DEM </td>
   <td style="text-align:left;"> C </td>
   <td style="text-align:left;"> House </td>
   <td style="text-align:left;"> VA </td>
   <td style="text-align:left;"> FALSE </td>
   <td style="text-align:left;"> TRUE </td>
   <td style="text-align:left;"> H </td>
   <td style="text-align:left;"> list("05") </td>
   <td style="text-align:left;"> CULLOP, BENJAMIN NIEL </td>
   <td style="text-align:right;"> 5 </td>
   <td style="text-align:left;"> list(2018) </td>
   <td style="text-align:left;"> C </td>
   <td style="text-align:left;"> DEMOCRATIC PARTY </td>
   <td style="text-align:left;"> 2017-07-02 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:left;"> Challenger </td>
   <td style="text-align:left;"> 2017-07-02 </td>
   <td style="text-align:left;"> 05 </td>
   <td style="text-align:left;"> C00649020 </td>
   <td style="text-align:left;"> CULLOP FOR CONGRESS </td>
   <td style="text-align:left;"> VANDEVER, JASON </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> H6VA05142 </td>
   <td style="text-align:left;"> 2017-01-01T00:00:00+00:00 </td>
   <td style="text-align:left;"> TRUE </td>
   <td style="text-align:left;"> 2018-04-08T00:00:00+00:00 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:left;"> PRE-CONVENTION </td>
   <td style="text-align:left;"> 201804169108269935 </td>
   <td style="text-align:left;"> transfers_from_other_authorized_committee </td>
   <td style="text-align:right;"> 0.00 </td>
   <td style="text-align:left;"> 2017-05-23T07:10:20 </td>
   <td style="text-align:left;"> 2017-05-16 </td>
   <td style="text-align:left;"> list(2016, 2018) </td>
   <td style="text-align:left;"> REP </td>
   <td style="text-align:left;"> C </td>
   <td style="text-align:left;"> House </td>
   <td style="text-align:left;"> VA </td>
   <td style="text-align:left;"> FALSE </td>
   <td style="text-align:left;"> TRUE </td>
   <td style="text-align:left;"> H </td>
   <td style="text-align:left;"> list("05", "05") </td>
   <td style="text-align:left;"> GARRETT, THOMAS ALEXANDER MR. JR. </td>
   <td style="text-align:right;"> 5 </td>
   <td style="text-align:left;"> list(2016, 2018) </td>
   <td style="text-align:left;"> I </td>
   <td style="text-align:left;"> REPUBLICAN PARTY </td>
   <td style="text-align:left;"> 2016-01-27 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:left;"> Incumbent </td>
   <td style="text-align:left;"> 2017-05-16 </td>
   <td style="text-align:left;"> 05 </td>
   <td style="text-align:left;"> C00607101 </td>
   <td style="text-align:left;"> TOM GARRETT FOR CONGRESS </td>
   <td style="text-align:left;"> WOODFIN, CHRISTOPHER MONTGOMERY MR. ESQ. </td>
   <td style="text-align:right;"> 2016 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2016 </td>
   <td style="text-align:right;"> 2018 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> H6VA05142 </td>
   <td style="text-align:left;"> 2016-01-01T00:00:00+00:00 </td>
   <td style="text-align:left;"> TRUE </td>
   <td style="text-align:left;"> 2016-12-31T00:00:00+00:00 </td>
   <td style="text-align:right;"> 2016 </td>
   <td style="text-align:right;"> 2016 </td>
   <td style="text-align:left;"> YEAR-END </td>
   <td style="text-align:left;"> 201702029042407932 </td>
   <td style="text-align:left;"> transfers_from_other_authorized_committee </td>
   <td style="text-align:right;"> 12889.20 </td>
   <td style="text-align:left;"> 2017-05-23T07:10:20 </td>
   <td style="text-align:left;"> 2017-05-16 </td>
   <td style="text-align:left;"> list(2016, 2018) </td>
   <td style="text-align:left;"> REP </td>
   <td style="text-align:left;"> C </td>
   <td style="text-align:left;"> House </td>
   <td style="text-align:left;"> VA </td>
   <td style="text-align:left;"> FALSE </td>
   <td style="text-align:left;"> TRUE </td>
   <td style="text-align:left;"> H </td>
   <td style="text-align:left;"> list("05", "05") </td>
   <td style="text-align:left;"> GARRETT, THOMAS ALEXANDER MR. JR. </td>
   <td style="text-align:right;"> 5 </td>
   <td style="text-align:left;"> list(2016, 2018) </td>
   <td style="text-align:left;"> I </td>
   <td style="text-align:left;"> REPUBLICAN PARTY </td>
   <td style="text-align:left;"> 2016-01-27 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:left;"> Incumbent </td>
   <td style="text-align:left;"> 2017-05-16 </td>
   <td style="text-align:left;"> 05 </td>
   <td style="text-align:left;"> C00607101 </td>
   <td style="text-align:left;"> TOM GARRETT FOR CONGRESS </td>
   <td style="text-align:left;"> WOODFIN, CHRISTOPHER MONTGOMERY MR. ESQ. </td>
   <td style="text-align:right;"> 2016 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2016 </td>
   <td style="text-align:right;"> 2018 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> H8VA05114 </td>
   <td style="text-align:left;"> 2017-04-01T00:00:00+00:00 </td>
   <td style="text-align:left;"> TRUE </td>
   <td style="text-align:left;"> 2018-04-15T00:00:00+00:00 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:left;"> PRE-CONVENTION </td>
   <td style="text-align:left;"> 201804239111725619 </td>
   <td style="text-align:left;"> transfers_from_other_authorized_committee </td>
   <td style="text-align:right;"> 146608.46 </td>
   <td style="text-align:left;"> 2017-10-01T20:55:35 </td>
   <td style="text-align:left;"> 2017-10-01 </td>
   <td style="text-align:left;"> list(2018) </td>
   <td style="text-align:left;"> DEM </td>
   <td style="text-align:left;"> C </td>
   <td style="text-align:left;"> House </td>
   <td style="text-align:left;"> VA </td>
   <td style="text-align:left;"> FALSE </td>
   <td style="text-align:left;"> TRUE </td>
   <td style="text-align:left;"> H </td>
   <td style="text-align:left;"> list("05") </td>
   <td style="text-align:left;"> HUFFSTETLER, ROGER DEAN RD </td>
   <td style="text-align:right;"> 5 </td>
   <td style="text-align:left;"> list(2018) </td>
   <td style="text-align:left;"> C </td>
   <td style="text-align:left;"> DEMOCRATIC PARTY </td>
   <td style="text-align:left;"> 2017-04-18 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:left;"> Challenger </td>
   <td style="text-align:left;"> 2017-10-01 </td>
   <td style="text-align:left;"> 05 </td>
   <td style="text-align:left;"> C00637918 </td>
   <td style="text-align:left;"> FRIENDS OF RD </td>
   <td style="text-align:left;"> JOHNSON, SARAH </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> H8VA05130 </td>
   <td style="text-align:left;"> 2017-04-01T00:00:00+00:00 </td>
   <td style="text-align:left;"> TRUE </td>
   <td style="text-align:left;"> 2018-03-31T00:00:00+00:00 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:left;"> APRIL QUARTERLY </td>
   <td style="text-align:left;"> 201804139108013236 </td>
   <td style="text-align:left;"> transfers_from_other_authorized_committee </td>
   <td style="text-align:right;"> 0.00 </td>
   <td style="text-align:left;"> 2017-10-16T21:00:02 </td>
   <td style="text-align:left;"> 2017-05-26 </td>
   <td style="text-align:left;"> list(2018) </td>
   <td style="text-align:left;"> DEM </td>
   <td style="text-align:left;"> C </td>
   <td style="text-align:left;"> House </td>
   <td style="text-align:left;"> VA </td>
   <td style="text-align:left;"> FALSE </td>
   <td style="text-align:left;"> TRUE </td>
   <td style="text-align:left;"> H </td>
   <td style="text-align:left;"> list("05") </td>
   <td style="text-align:left;"> SLATE, ADAM </td>
   <td style="text-align:right;"> 5 </td>
   <td style="text-align:left;"> list(2018) </td>
   <td style="text-align:left;"> C </td>
   <td style="text-align:left;"> DEMOCRATIC PARTY </td>
   <td style="text-align:left;"> 2017-05-26 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:left;"> Challenger </td>
   <td style="text-align:left;"> 2017-05-26 </td>
   <td style="text-align:left;"> 05 </td>
   <td style="text-align:left;"> C00639153 </td>
   <td style="text-align:left;"> ADAM SLATE FOR CONGRESS </td>
   <td style="text-align:left;"> MCREYNOLDS, JAMES M. </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
   <td style="text-align:right;"> 2018 </td>
  </tr>
</tbody>
</table></div>

